HPC--101\\Onboarding

### 2023-05-03 hpc_101/sections/09_appendix.tex
monitoring examples added

@@

>>>>

\end{frame}
\section{Monitoring Jobs and Partitions}{Monitoring Jobs and Partitions}
\begin{frame}[fragile]
\frametitle{Monitoring Running Jobs}
\begin{block}{\textbf{squeue}}
\begin{semiverbatim}\tiny \texttt
[victorgc@node-0093 HDM]\$ squeue --me
             JOBID PARTITION     NAME     USER ST       TIME  NODES NODELIST(REASON)
          43486015   sandbox     bash victorgc  R    2:05:37      1 node-0093
\end{semiverbatim}
\end{block}
The --me flag can be removed and \textbf{squeue} will report all running jobs in the system.
\begin{block}{\textbf{squeue}}
\begin{semiverbatim}\tiny \texttt
[victorgc@node-0093 HDM]\$ squeue | head
             JOBID PARTITION     NAME     USER ST       TIME  NODES NODELIST(REASON)
          43078226   bioinfo    sgSQL     user  R 23-02:12:35      1 node-0327
          43078227   bioinfo cromwell     user  R 23-02:12:09      1 node-0327
          43485890   bioinfo       QC     user  R    4:45:59      1 node-0327
          43399271   bioinfo      TQC     user  R 3-20:49:10      1 node-0328
          43485868 exclusive    MoSe2     user  R    5:20:14      1 node-0296
          43485867 exclusive    MoSe2     user  R    5:30:46      1 node-0295
          43485866 exclusive    MoSe2     user  R    5:35:43      1 node-0294
          43485815 exclusive    MoSe2     user  R    5:57:03      1 node-0281
\end{semiverbatim}
\end{block}
\numlessfootnotetxt{\tiny \href{https://slurm.schedmd.com/squeue.html}{https://slurm.schedmd.com/squeue.html}}

@@

\begin{frame}[fragile]
\frametitle{Completed Jobs Reports}
\begin{block}{\textbf{sacct}}
\begin{semiverbatim}\tiny \texttt
[victorgc@node-0093 HDM]\$ sacct -u victorgc -X | head
JobID           JobName  Partition    Account  AllocCPUS      State ExitCode
------------ ---------- ---------- ---------- ---------- ---------- --------
43486049_1     spectrum     shared         uh          1  COMPLETED      0:0
43486049_12    spectrum     shared         uh          1  COMPLETED      0:0
\end{semiverbatim}
\end{block}
\begin{block}{\textbf{seff}}
\begin{semiverbatim}\tiny \texttt
[victorgc@node-0093 HDM]\$ seff 43486049_12
Job ID: 43486061
Array Job ID: 43486049_12
Cluster: uh_hpc
User/Group: victorgc/victorgc
State: COMPLETED (exit code 0)
Cores: 1
CPU Utilized: 00:00:33
CPU Efficiency: 97.06\% of 00:00:34 core-walltime
Job Wall-clock time: 00:00:34
Memory Utilized: 75.91 MB
Memory Efficiency: 1.27\% of 5.86 GB
\end{semiverbatim}
\end{block}
The output of \textbf{sacct} is highly customizable.
\numlessfootnotetxt{\tiny \href{https://slurm.schedmd.com/sacct.html}{https://slurm.schedmd.com/sacct.html}}

\begin{frame}[fragile]
\frametitle{Partition Information}
\begin{block}{\textbf{sinfo}}
\begin{semiverbatim}\tiny \texttt
[victorgc@node-0093 HDM]\$ sinfo | head
PARTITION       AVAIL  TIMELIMIT  NODES  STATE NODELIST
gpu                up 3-00:00:00      9    mix gpu-[0013,0017-0024]
gpu                up 3-00:00:00      1  alloc gpu-0016
sandbox            up    4:00:00      1    mix node-0093
sandbox            up    4:00:00      3  alloc node-[0094-0096]
shared*            up 3-00:00:00      4  down* node-[0102,0120,0122,0178]
shared*            up 3-00:00:00      8  drain node-[0111-0112,0126,0130,0150,0175,0344,0350]
\end{semiverbatim}
\end{block}
Partition information can be printed in a per node basis.
\begin{block}{\textbf{sinfo}}
\begin{semiverbatim}\tiny \texttt
[victorgc@node-0093 HDM]\$ sinfo -Nel | head
Wed May 03 01:20:33 2023
NODELIST   NODES       PARTITION       STATE CPUS    S:C:T MEMORY TMP_DISK WEIGHT AVAIL_FE REASON
gpu-0001       1     gpu-sandbox       mixed 20     2:10:1 128500        0  10000 x86,inte none
gpu-0001       1  kill-exclusive       mixed 20     2:10:1 128500        0  10000 x86,inte none
gpu-0001       1     kill-shared       mixed 20     2:10:1 128500        0  10000 x86,inte none
gpu-0002       1  kill-exclusive        idle 20     2:10:1 128500        0  10000 x86,inte none
gpu-0002       1     kill-shared        idle 20     2:10:1 128500        0  10000 x86,inte none
\end{semiverbatim}
\end{block}
\numlessfootnotetxt{\tiny \href{https://slurm.schedmd.com/sinfo.html}{https://slurm.schedmd.com/sinfo.htmls}}
\end{frame}
